---
title: "The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction"
subtitle: "Nowhere near done yet! We had significant issues with our last dataset and had to restart, so bare with us."
author: 
  - Sami El Sabri
  - Liban Timir
thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis. SSRP replication available at: https://www.socialsciencereproduction.org/reproductions/94caaeaf-7e11-4efa-9269-7729fc2e0837/index"
date: 02-13-2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(ggplot2)

```


# Introduction

In recent years, the intersection between personal beliefs in free will and cognitive behavioral outcomes has emerged as a pivotal area of psychological inquiry. While the existence of free will is a highly theoretical and philosophical question, the belief in free will has undeniable effects on various other psychological constructs such as autonomy, meaningfulness, and self-efficacy (@baumeister2014, @alquist2013). Despite the robustness of these relationships, there remain gaps in the literature of the specific dynamics of these effects and the generalizability in field settings. @feldman2017 conducted a study investigating the effects of the belief in free will on job satisfaction and attempted to draw cross-cultural and longitudinal conclusions on the positive correlation between the belief in free will and job satisfaction. 

They executed three distinct studies: the first with real estate agents in Taiwan over three months, the second involving American workers over six months using Amazon Mechanical Turk, and the third utilizing a large cross-cultural sample from the World Values Survey encompassing 16 countries. This multifaceted approach allowed them to assess the generalizability of free will beliefs as predictors of job satisfaction across various cultural contexts and professional environments, providing a robust examination of how these beliefs influence job satisfaction over time. 

Utilizing the same dataset and a similar methodology to Feldman et al. (2017), we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality. While Feldman et al. did investigate the relationship between the belief in free will and job satisfaction in the United States, they did not integrate these results to the cross-cultural analysis, as the US were not included in the sample of 16 countries. This paper, therefore, seeks to fill this gap and reproduce these aspects of the Feldman et al. paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey. The estimand is the correlation between the belief in free will and job satisfaction. Our reproduction was conducted using the statistical programming language R (@citeR). In the data analysis and visualization process, we also made use of the following R packages: tidyverse (@citetidyverse), dplyr (@citedplyr), knitr (@citeknitr), kableExtra (@citekExtra), and countrycode (@citecc). 

We begin our paper with a closer look at the data source and measurement (@sec-data), followed by a selection of relevant results (@sec-results). Finally, we will conclude with a discussion of our findings to integrate our replication with the original paper by @feldman2017 and the broader literature on free will beliefs. We will also discuss potential ethical biases, limitations, and future directions. This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States. ### TALK ABOUT FINDINGS HERE###


# Data {#sec-data}
## Source {#sec-source}
Dataset Overview:

Introduction to the Dataset: Start by providing a brief overview of the dataset(s) used, including the source (e.g., Amazon Mechanical Turk, World Values Survey) and the rationale for selecting these datasets for replication.
Scope and Scale: Mention the size of the dataset, the number of participants, and the time frame covered by the data collection.
## Measurement {#sec-measurement}
Variables Description:

Dependent Variable(s): Describe the main variable of interest, job satisfaction, including how it was measured or operationalized in the dataset.
Independent Variable(s): Explain the measurement of free will beliefs and any other relevant variables that were analyzed as predictors or controls in the study (e.g. job autonomy, self-efficacy etc.)

Covariates and Controls: If applicable, detail any additional variables used as controls or covariates in your analysis, such as demographic information, employment characteristics, or cultural factors.

GO INTO GREAT DETAIL WITH MEASUREMENT!

## Data Characteristics {#sec-characteristics}

Preprocessing Steps: Outline the steps taken to prepare the data for analysis, including any cleaning, filtering, or transformation processes.
Handling of Missing Data: Describe how missing data were addressed, whether through imputation, exclusion, or another method.

Summary Statistics and Initial Observations:

Descriptive Statistics: Provide summary statistics for the main variables, including means, standard deviations, and ranges. This gives readers a sense of the data's central tendencies and variability.
Visualizations: Include graphs or tables that offer an initial view of the data, such as distributions of job satisfaction and free will beliefs. Discuss any notable patterns or preliminary observations.
Comparative Analysis (if applicable):

Comparison with Original Study: If you have access to summary statistics or data visualizations from the Feldman et al. study, briefly compare those findings with your dataset to highlight similarities or differences.
Rationale for Differences: Discuss any expected or surprising differences in the data between the original study and your replication effort, potentially attributable to cultural or temporal differences.



#####

The dataset for the study provides a detailed snapshot of free will beliefs, job satisfaction, and perceived job autonomy among American online workers. 

The variables within this dataset were carefully selected to reflect key indicators of job satisfaction, belief in free will, job autonomy, and additional agency constructs for regional analysis within America. 

Data cleaning was especially important in this case, considering the challenges inherent in longitudinal and generational health data. This ensured the integrity and continuity of data across different time points and handling any missing or inconsistent records. The dataset underwent meticulous cleaning using R [@citeR], addressing missing values and ensuring consistency across responses. Special attention was given to the reliability of scales used for measuring the core variables, with adjustments made to account for the online work setting of the participants.

Summary statistics revealed the mean and median job satisfaction rates, the correlation in job autonomy, and other job-related metrics. This aggregated data provided a foundation for understanding the base conditions of the workplace and any preliminary patterns indicating the persistence of individual agency.

Visual representations, such as graphs and tables, illustrated the distribution of job satisfaction, free will beliefs, and the relationship between the two. These visuals helped to convey the depth and nuances of the autonomy persistence observed in the American data.

The appendices include detailed statistical tables, additional graphs showing complex data relationships, and extensive notes on the data cleaning and processing methodology.

This description of the dataset was written with the general ethical practices of demographic research in mind and provides a narrative for a subset of data focused on America.




```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

```

Talk way more about it. 






# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

```





\newpage


# References


